Circumcision Paper Text

### 2024-04-11 paper/paper_cals.Rmd
Add five year age group comparisons for VMMC countries

## Subnational Variation in Total, Medical \& Traditional Circumcision across different ages

@@

Age at circumcision differed greatly by circumcision type and location. 
The age group which experienced the greatest increase in MC coverage from 2006, the year before VMMC programme implementation began (reference), to 2020 was 
x, 
reflecting VMMC focus on these ages. 
The age group with the highest MC coverage in 2020 was 
x, 
in contrast to 2006, where this age group was 
x. 
The age group with the highest MMC coverage in 2020 was 
x, 
while for TMC coverage this age group was 
x. 
The average age of MC in 2020 in SSA was 
x, 
compared to 
x 
in 2006. 
For MMC, the average age at circumcision in 2020 was 
x, 
compared to 
x 
in 2006, while for TMC the average age was 
x 
in 2020, compared to 
x 
in 2006. 
The average age of MC in 2020 for ESA was 
x, 
while in WCA it was 
x.

@@

Fill in!

@@

x
/
x
 districts in these countries were e
x
pected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from 
x
/
x
 in 2006, before VMMC programmes began. 
Even in 
x
, where MC was projected to be lowest in 2020, 
x
/
x
 districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
MC coverage there increased from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase.

>>>>

## Subnational Variation in total, medical \& traditional circumcision across different ages

```{r, echo = FALSE}
x2 <- readRDS("data/inlines/02_inlines.RDS")
for (i in seq_along(x2)) {
  assign(names(x2)[i], x2[[i]])
}
age_group_cov <- sapply(
  age_group_cov, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
age_group_cov_non_vmmc <- sapply(
  age_group_cov_non_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
age_group_cov_vmmc <- sapply(
  age_group_cov_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
```

@@

Age at circumcision differed greatly by circumcision type and location. 
The five-year age group in 2006, the year before VMMC programme implementation began, 
which had the highest MC coverage across the SSA region was
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(age_group)`, 
at 
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_percentage()`
)
. 
In contrast, the age group with the highest MC coverage in 2020 was 
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(age_group)`,
at
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_percentage()`
).
The five-year age group in 2006 which had the highest MMC coverage was
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(age_group)`, 
at 
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(upper) %>% to_percentage()`
)
. 
The age group with the highest MMC coverage in 2020 was also
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(age_group)`,
, now at
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(upper) %>% to_percentage()`
).
The five-year age group in 2006 which had the highest TMC coverage was
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(age_group)`, 
at 
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_percentage()`
)
. 
The age group with the highest TMC coverage in 2020 was
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(age_group)`,
,
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_percentage()`
).
This decrease in the five-year age group with the highest MC coverage, increase in the 
age group for TMC with the highest coverage (as well as a decrease in coverage for 
the highest five-year age group), and increase in overall MMC coverage across the SSA region is 
indicative of the effect of VMMC programme implementation on the region.

<!-- TODO Still: 
- 15-29 year olds increase in MC/TMC/MMC (already written about?)
- Contrast to 30-49 year olds somehow, showing different patterns of circ
(increasing more for MC/MMC, decreasing more for TMC)
- Compare differences in VMMC and non-VMMC, in terms of the above
-->
We may compare changes in circumcision amongst two age groups; 15-29 year olds, which 
are a particular focus for VMMC implementation, and 30-49 year olds, which are not. 
MC coverage amongst 15-29 year olds increased from 
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
) in 2006
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020. 
In contrast, MC coverage amongst 30-49 year olds only increased from 
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
) in 2006
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020. 
Therefore, MC coverage across SSA saw greater increases in this younger age group than in this older one, in line 
with VMMC programme age focus. 
Similarly, MMC coverage amongst 15-29 year olds increased from 
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
) in 2006
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, while MMC coverage amongst 30-49 year olds increased from 
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
) in 2006
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020. 
Therefore, MMC coverage across SSA also saw greater increases amongst 15-29 year olds 
than amongst 30-49 year olds. 
The changes seen in TMC, however, contrast to these larger increases in MC and MMC coverage for 15-29 year olds. 
TMC coverage amongst 15-29 year olds decreased from 
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
) in 2006
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020, while TMC coverage amongst 30-49 year olds decreased from 
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
) in 2006
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
) in 2020. 
Thus, TMC coverage decreased less in absolute terms amongst 30-49 year olds than amongst 
15-29 year olds, which is line with the greater focus on performing MMCs amongst this 
younger age group.

Finally, we can contrast patterns in circumcision pattern for different age groups
amongst VMMC and non-VMMC priority countries, where differences in 2006 and 2020 
levels and patterns of circumcision seem to be more pronounced.

<!-- For VMMC countries, five year age group MC, MMC, TMC -->
For VMMC priority countries, five-year age group MC coverage in both 2006 and 2020 was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
) and 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
(
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
), respectively. 
However, in 2006 MMC coverage was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
 year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
). 
This contrasts with 2020, where MMC coverage was highest amongst 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
 year olds, at
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
 (
x
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
 - 
x
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
), showing a shift upwards in age for MMCs in VMMC priority countries, as a result of VMMC focus on young adults. 
In 2006, TMC coverage was greatest in 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
). while in 2020 it was most prevalent in
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
year olds, at 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
 (
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
 - 
`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`, highlighting a shift upwards in TMCs in VMMC priority countries, 
likely resulting from previously TMCs being performed as TMCs.

For non-VMMC countries, five year age group MC, MMC, TMC

Similarly, we can compare the 2006 and 2020 circumcision levels amongst 15-29 and 30-49 year olds
in both VMMC and non-VMMC countries, respectively.

@@

Fill in! 
- Talk mainly about average age at which MCs/MMCs/TMCs performed in 2006 and 2020
- Also compare VMMC and non-VMMC

The mean age at circumcision for MC in 2006 was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
Similarly, the mean age at circumcision for MMC in 2006 was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
Finally, the mean age at circumcision in 2006 for TMC was 
x
(
x
- 
x
), while in 2020 it was
x 
(
x
-
x
).
So the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
However, it is important to note that the uncertainty ranges in our credible intervals 
overlap, so this increase is ?. 
In constant, the mean age at circumcision for TMC decreased. 
This may suggest that VMMC implementation amongst 15-29 year olds has 
corresponded to an upward shift of mean age at circumcision for MC and MMC, and 
replaced some circumcisions which would previously have been performed as TMCs, 
which may explain the observed decrease in mean age of TMC.

What is the narrative here?
- For SSA, MC and MMC age goes up, TMC goes down
- For VMMC, average age for all substantially higher, but follows same pattern. 
  Could be argued that this is because people previously receiving TMCs are now receiving MMCs, 
  pushing mean age of TMC down further. 
- For non-VMMC, ages substantially lower. 
  MMC age actually decreases, suggesting MMC-nT occuring, replacing TMC!

@@

x
/
x
 districts in these countries were e
x
pected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from 
x
/
x
 in 2006, before VMMC programmes began. 
Even in 
x
, where MC was projected to be lowest in 2020, 
x
/
x
 districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
MC coverage there increased from 
x
(
x
to 
x
) in 2006 to 
x
(
x
to 
x
) in 2020, a 
x
(
x
to 
x) increase.
